# **2** | Simon Experiment 
First, download the [SimonEffect.zip](PsychoPy/2.SimonEffect.zip) folder and unpack it, then open the folder and open the 'SimonEffect_experiment.psyexp' PsychoPy file. 

We are already starting to get a little more complicated with our PsychoPy experiments. Run the experiment before you start editing it by pressing the play button, entering any participant number, and pressing 'ok'. In this experiment you are first given some instructions and then asked to respond to 'green' and 'red' circle stimuli. The Simon effect is an effect of reaction times - people are faster at responding with their left hand, on the left, when a stimulus is on the left - same for the right side too. This is compared to when you must make a response using your hand on the opposite side of a stimulus. This little experiment will actually generate some data!  

As it stands, the experiment will first, give you some instructions then run you through two 'congruent' trials - were the side of the stimuli and the side of the response match. After that it will end. 

## What you learn

The idea is that making changes to the PsychoPy experiment will help you get a feel of changing parameters within components, routines and loops. This introductory experiment is aimed at helping you:

* Modifying components of loops, routines and components.
* Modifying Excel file to result in changes in the experiment. 
* Modifying routine's length.
* Adding correct answers.

## Things to change

Let's see if you can make a few changes and perhaps even get some simple data to look at. 

1.\ Can you add two more trials in the 'incongruent' condition - so that a red circle appears on the right in one trial and a green circle on the left in another trial?
`r hide("Hint")`
```{r,echo = FALSE, results='asis'}
cat("You will need to modify the Excel file save it and upload it again to the trials loop. You want two more trials that are in effect the opposite of what you see for the congruent trials.")
```
`r unhide()`


2.\ Once you've added more conditions, make sure they appear in a random order and add more repetitions of trials; so that the number of trials per condition repeat - set it for 5 repetitions per condition. 
`r hide("Hint")`
```{r,echo = FALSE, results='asis'}
cat("You can change all of this by manipulating the properties of the 'trials' loop.")
```
`r unhide()`

3.\ At the moment the stimuli stays on the screen until a response. To increase errors and speed up responses can you have set a time limit so that the participant only has 2 seconds to respond? 
`r hide("Hint")`
```{r,echo = FALSE, results='asis'}
cat("You can change all of this by manipulating the properties of the components within the 'trial' routine.")
```
`r unhide()`

4.\ Can you manipulate the 'key_resp' component in the 'trial' routine so that it stores the correct answer?
`r hide("Hint")`
```{r,echo = FALSE, results='asis'}
cat("As well as modifying the properties in 'key_resp' Data tab, you will also have to make some changes to the spreadsheet so that you can identify what response is correct in any given condition.")
```
`r unhide()`

## Test yourself

```{r, echo = FALSE, results = 'asis'}

opts <- c(answer = "'q', 'p'", 
            "'q,p'", 
            "'q-p'", 
            "Q,P")

q1 <- mcq(opts)

cat("**Question 1** | If you wanted to allow the letters p and q as a response (instead of a and k) what would you type in the 'Allowed keys' section of the response properties?","<br><br>", q1)
```


```{r, echo = FALSE, results = 'asis'}

opts <- c("#", 
            "£", 
            "&", 
            answer = "$")

q1 <- mcq(opts)

cat("**Question 2** | In the 'trial' component, the 'left_stim' and 'right_stim' components get their colour from the spreadsheet. What symbol tell PsychoPy that the colour is listed in the spreadsheet?","<br><br>", q1)
```

```{r, echo = FALSE, results = 'asis'}

opts <- c("Constant", 
            "Set every frame", 
            answer = "Set every repeat")

q1 <- mcq(opts)

cat("**Question 3** | If you want any property of a component to change on a trial-by-trial basis which of the following should you select?","<br><br>", q1)
```
